Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-10-17 paper/virtual_cytoplasm_v2.tex
comments are removed from the text except one which needs to be addressed by Leandro

While the structure and dynamics of biomolecules is well characterized
\textit{in vitro}, the understanding of the influences of crowded
environments \textit{in vivo} are still evolving.  Techniques such as
nuclear magnetic resonance~\cite{reckel2007,pielak2008} and
fluorescence spectroscopy~\cite{ignatova2004,xie2008,English2011} are
among the most relevant to the field due to their ability to probe
cells in a non destructive way. Another essential class of methods
come from computational modeling and simulation. By extrapolating the
advances in computational power in the last decades to the future, it
was estimated that the atomistic simulation of an entire
\textit{Escherichia coli} bacterium for \SI{1}{\nano\second} will be
possible in 15 years from now~\cite{vanGunsteren2006a}. {\bf THAT WAS
  13 YEARS AGO. WHAT IS THE STATE OF THE ART?} {\color{blue} The paper predicts that simulating a whole E. coli bacterium with $10^{11}$ atoms for 1 ns will be possible in 2034, thus the "15 years from now" in our text. That was meant as an introduction to the simulation of big systems. The evolution of computational models to study crowing and the state-of-the-art is discussed in the next paragraph. Maybe we can move this phrase to the beginning of the next paragraph }

@@

\subsection{Analyses}
For statistics, the average and standard error of the three trajectories are reported. For values that
are specific to each chain, we used the average over the individual
chains in each trajectory of the replicas. Additionally, since there
is more than one copy of some crowders in the cytoplasm models,
average values and standard errors are calculated {\bf DO YOU MEAN THE
  AVERAGE OVER ALL COPIES? considering each copy of each replica}
independently {\color{blue} Yes, the averages are calculated over all copies of each crowder in all replicas}. As in the dilute system, separate chains of each copy
of the crowders were considered as independent samples when running
analyses that focus on one single chain. The first half of all
simulations was discarded as equilibration time and analyses used only
the second half.

Analyses were done using GROMACS tools after removing artifacts
generated by periodic boundary conditions from the trajectories. A
Mean Square Displacement (MSD) analysis was performed to calculate the
translational diffusion coefficient, which were extracted by a linear
fit to MSD by averaging blocks with a length of $10\, ns$ for dilute systems and $100\, ns$ 
for cytoplasm system~\cite{Allen1987a}. In principle, diffusion
coefficient needs to be corrected for finite size
effects~\cite{Yeh2004} but due to relatively large simulation boxes
this correction is negligible {\bf NOT FOR PROTEINS THAT DIFFUSE
  SLOWLY!}. {\color{blue} The correcion in Yeh2004 is derived for cubic simulation boxes, in our single molecule simulations we have non-cubic boxes, one needs to derive the correction from Eq 11 in Yeh2004. My Mathematica skills are rusty now, could you do that? If you think it's absolutely necessary} Root Mean Square Deviation (RMSD) and Root Mean Square
Fluctuation (RMSF) calculations considered the C$\upalpha$ atoms only for analysis in each trajectory
{\bf ARE YOU SURE? THE DEFAULT IS TO TAKE THE AVERAGE STRUCTURE. OR DO
  YOU MEAN THE STRUCTURE FOR FITTING?} {\color{blue} I checked and indeed we used the average structure calculated with the second half of the trajectories. I removed "the reference frame for RMSF was the midpoint of the time interval" from the text. The information about the second half of the trajectory is in the previous paragraph, which is about statistics}. The chain interface area of a given oligomer in a given
frame was calculated as the difference between the solvent exposed
surface area (SASA) of the oligomer in that frame and the sum of the
SASAs of each of its chains independently in that same frame. Other
analyses, such as box volume and Radial Distribution Function (RDF),
followed standard procedures.

@@

\begin{table}[H]
\centering
\caption{Protein, PDB ID, number N of proteins in the simulation. 
Fraction of the total abundance of non-ribosomal proteins in the cytosol of {\em
    E. coli} K12 and oligomeric state of each protein that was
  selected to compose our cytoplasm model. {\bf WRITE OUT WHOLE
    PROTEIN NAMES}}
\label{tbl:protein_fraction}
\begin{tabular}{ccccc}
\hline
Protein & PDB & N & Fraction [\%] & State\\
\hline
{\color{blue}Elongation factor TU} (TufA) & 1DG1~\cite{Abel1996}       & 6 & 19.7 &  dimer \\
{\color{blue}Cobalamin-independent methionine synthase} (MetE) & 1U22~\cite{Ferrer2004}     & 7 & 11.6 &  monomer \\
{\color{blue}Isocitrate dehydrogenase} (IcdA) & 1P8F~\cite{Mesecar2000}    & 2 & 4.7  &  dimer \\
{\color{blue}Alkyl hydroperoxide reductase subunit C} (AhpC) & 1YEP~\cite{Parsonage2005}  & 1 & 4.1  &  decamer \\
{\color{blue}Cold-shock protein} (CspC) & 1MJC~\cite{Schindelin1994} & 3 & 4.0  &  monomer \\
{\color{blue}Pyrophosphatase} (Ppa)  & 2EIP~\cite{Kankare1996}    & 1 & 2.9  &  hexamer \\
{\color{blue}Glyceraldehyde 3-phosphate dehydrogenase A} (GapA) & 1S7C~\cite{ShinXXX}        & 1 & 2.1  &  tetramer \\
{\color{blue}Enolase} (Eno)  & 1E9I~\cite{Kuhnel2001}     & 1 & 1.9  &  dimer \\
\hline
Total &                           & 48& 51.1 & \\
\hline
\end{tabular}
\end{table}

@@

\subsubsection{Structural integrity}
The structure of the individual chains of the crowders that were used
in our cytoplasm model were not affected to a great extent by the
crowded environment. The values of their root mean square deviation considering only
their C$\upalpha$ in the cytoplasm model {\color{blue} increased by less than 11\% when compared to the dilute condition} {\bf WHAT DOES WITHIN 11\% MEAN?}, except for
TufA, MetE and IcdA, which have RMSD values 105, 25 and 33\% higher in
the crowded environment than in the dilute condition {\color{blue}(Fig.~\ref{fig:structural_integrity_chain}A)}. {\bf ARE THERE
  RMSD PLOTS? REFER TO THEM.} {\color{blue} Visual inspection of the final frames of the simulations of these crowders in the cytoplasm model and in dilute condition revealed that, for TufA, the conformational differences are on the $\upbeta$-hairpin around residues 40-62. This region is called Switch I and is known to be flexible and to display conformational changes due to interactions with the ribosome or other partners~\cite{Abel1996}. For MetE, there are differences in the conformation of the loop around residues 450-460 and in the C-terminal $\upalpha$-helices. This loop is known to be flexible and was not modeled in the crystallographic structure due to such flexibility~\cite{Ferrer2004}. For IcdA, the differences are located at the N-terminal coil formed by residues 1-8.}

@@

\subsubsection{Structural dynamics}
{\bf THIS PARAGRAPH REPEATS AND CONTRADICTS ITSELF. IS FLEXIBILITY
  AFFECTED OR NOT? FROM THE GRAPH I WOULD SAY THE THE FIVE PROTEINS
  NOTED BELOW ARE MUCH MORE FLEXIBLE, NOT SLIGHTLY. ONE WAY OF
  QUANTIFYING THIS IS TO COMPUTE THE AVERAGE OF THE MEAN SQUARE
  FLUCTUATION OVER THE WHOLE PROTEIN, THAT IS BEFORE TAKING SQUARE
  ROOTS OF COURSE AND PLOTTING THAT IN A BAR GRAPH.} {\color{blue} Overall, flexibility (meaning the values of RMSF for each residue) is affected in some cases, but the flexibility profile (meaning the overall shape of the RMSF plot) is not. Maybe that was the source of the apparent contradiction. I changed the text to clarify that. I also removed words such as "slightly" and "small" from the text.}

@@

We found that completely protonating the phosphate groups of ATP and
FBP is enough to prevent their aggregation with Mg$^{2+}$. While RDFs
show that ATP$^{-3}$ and FBP$^{-4}$ aggregate around Mg$^{2+}$
(Fig.~\ref{fig:avoiding_aggregation}A), this is not observed for
ATPH\textsubscript{3} and
FBPH\textsubscript{4}(Fig.~\ref{fig:avoiding_aggregation}B-C).  {\bf
  WERE ANY INTERMEDIATE PROTONATIONS TESTED? E.G. FBPH2(2-) AND ATPH(2-)?
  COMPLETELY PROTONATING IS UNPHYSICAL AS WELL AT THE PH STUDIED. FOR E COLI THE PH SHOULDBE ROUGHLY 7.4 https://en.wikipedia.org/wiki/Cytosol} {\color{blue}I didn't try intermediate protonations, but this can be done in about 1 week if necessary. The physiological states of FBP and ATP at pH 7.4 would be the ones we used originally in the soup. So, in this sense, any protonated state could be called unphysical or unrealistic. We discuss the tradeoffs of using this unphysical protonated state in the discussion section}

@@

\section*{Discussion}\label{sec:dissc}
The main difference between the behavior of the macromolecules that
compose our model in the crowded system and in the dilute condition is
their translational diffusion coefficient, which drops by around
85\% for the proteins and 93\% for the tRNA
(Fig.~\ref{fig:translational_diffusion}A). The slope of the line
generated by fitting a linear regression model to values of
$D_{cyto}/D_{dil}$ is close to zero (slope $= 0.00028$), showing that
the drop in diffusion coefficient is independent of the size of the
macromolecules. We found that the aggregation of ATP$^{-3}$ and
FBP$^{-4}$ around Mg$^{2+}$, which was used as counter-ion for tRNA,
leads to an exaggerated confinement of the tRNA molecules.  Therefore,
tRNA is considered as an outlier in the duffusion calculations. In
fact, the slope of the linear regression line fitted to
$D_{cyto}/D_{dil}$ is reduced by by 50\% and gets even closer to zero
(slope $= 0.00014$) after removing the diffusion coefficient of tRNA
from the data. These data are in agreement with experimental results
showing that the translational diffusion coefficient of Green
Fluorescent Protein (GFP) in {\em E. coli}, as measured by
fluorescence recovery after photo-bleaching (FRAP), decreased 90\%
when compared to {\em in vitro}
measurements~\cite{Elowitz1999,Konopka2006}.
{\bf IT MAY BE NECESSARY TO DISCUSS RMSF HERE AS WELL} {\color{blue} This first paragraph is focused on validation of the cytoplasm model by comparison with experimental results, which are available for the translational diffusion coefficient. We don't have specific experimental data that we can compare our RMSF data to. Should we add RMSF here anyway? There is a discussion about our RMSF results some paragraphs ahead in which we compare our data with general trends that were experimentally observed.}

@@

Previous
all-atom simulations of {\color{blue} large} scale {\bf WHAT DO YOU MEAN WITH HIGH
  SCALE?} {\color{blue} corrected to large scale} cytoplasm models used parameters from the CHARMM family of
force fields~\cite{Yu2016a}. In this work we use a modified version of
the AMBER FF99SB force field in which the solvent-solute interactions
are 10\% stronger~\cite{Best2014a} to study crowding effects on a
cytoplasm model. This force field was chosen because it was corrected
to reproduce experimental data when there are many proteins in the
same simulation box. All-atom explicit solvent molecular dynamics
simulations have been reported for large-scale cytoplasm models of
\textit{Mycoplasma genitalium} composed of 103- and 12-million atoms
that were simulated for 20 and 60 \SI{}{\nano\second},
respectively~\cite{Yu2016a}. The cytoplasm model described in this
work has 1.5 million atoms and was simulated for the total of
\SI{3}{\micro\second}, an unprecedented time scale to study crowding
effects on a heterogeneous cytoplasm model in atomic detail.  {\bf ADD
  REFERENCES TO THE NEW FEIG PAPERS AND ZAHEDEHS ACS OMEGA PAPER UNDER
  REVIEW. WE WILL SEND IN THAT ONE AS SUPPORTING MATERIAL FOR REVIEW
  ONLY.}

Three crowders (TufA, MetE and IcdA) displayed greater deviation from
their crystallographic structure in the cytoplasm model when compared
to the dilute condition, indicating that there was some degree of
local unfolding
(Fig.~\ref{fig:structural_integrity_chain}A). Interestingly, oligomers
were marginally less stable {\color{blue} in the cytoplasm model} {\bf THAN WHAT? Monomers?} {\color{blue} oligomers in the cytoplasm were marginally less stable than oligomers in the dilute condition. Added "in the cytoplasm model" to the text.}
(Fig.~\ref{fig:structural_integrity_chain}B) and the flexibility
profiles calculated considering the C$\upalpha$ for each chain of the
elements of our cytoplasm model show that, in the crowded condition,
most of the proteins (TufA, MetE, AhpC, CspC and Ppa) are more flexible than in the dilute condition (Fig.~\ref{fig:rmsf}). This
is in agreement with previous simulations~\cite{Feig2011} and
experiment~\cite{miklos2011,Wang2012b} showing that crowders can
destabilize the native structure of proteins due to the numerous
unspecific short-lived interactions that are formed between them in a
crowded environment. A study of protein properties at increasing
concentration showed only few interactions between proteins of the
same type~\cite{Bashardanesh2019a}. {\color{blue} We highlight that there are no specific interactions described between the proteins that were used in our cytoplasm model.} {\bf do we expect specific interactions between the proteins in our cyto model? In that case write that with references, otherwise write that there are no known specific interactions between these proteins.} {\color{blue} The only specific interaction we antecipate between the components of the soup is that TufA interacts with tRNA (PDB ID 1TTT is an example of such complex). However, since we are ignoring tRNA in our analyses, I did't mention it. PS: I checked and the TufA-tRNA complex is not present in the last frames of our replicas.}

Magnesium cations were added to our cytoplasm model as counter-ions
for tRNA and ATP. However, as the simulation progressed, FBP and ATP
aggregated around Mg$^{2+}$ and, by consequence, around tRNA{\bf,
  effectively removing the counter ions from the RNA. IS THAT
  CORRECT?} {\color{blue} No, Figure \ref{fig:tRNA_aggregation} shows that Mg$^{2+}$ is still concentrated around tRNA in the soup }. After identifying this problem, we used simulations of
small systems containing only the metabolites, Mg$^{2+}$ and water to
test different strategies to prevent aggregation in future studies
using long simulations of cytoplasm models. We found that protonating
the phosphate-containing metabolites is enough to reach this goal
(Fig.~\ref{fig:avoiding_aggregation}). Even though ATPH$_3$ and
FBPH$_4$ are not the biologically relevant forms of these molecules in
physiological pH, using their protonated forms may be an acceptable
compromise between parametrization complexity and practical
results. The biggest impact of this approach is on long range
interactions of these metabolites with other molecules due to the
neutralization of their net charge. However, molecules in a crowded
environment are restrained to smaller volumes and shorter inter
molecular distances, which mitigates the effect of charge
neutralization. It has been suggested that charged species should
employ scaled charges in order to be compatible with the empirical
water models~\cite{Leontyev2009a,Leontyev2011a}. Due to the high local
density of negative charges in FBP and ATP this might indeed be an
alternative solution, barring use of polarizable
models~\cite{Ponder2010a,Lopes2013a,Ghahremanpour2018b,Walz2018a}.

To the best of our knowledge, {\bf AGAIN CHECK LATEST FEIG PAPERS} {\color{blue} Latest Feig paper is not a cytoplasm model~\cite{nawrocki2019}}
there is only published study on large scale cytoplasm models that
included metabolites with all-atom explicit solvent molecular
dynamics~\cite{Yu2016a}. Although these authors did not report
aggregation, they mention that the translational diffusion of highly
charged phosphate-containing metabolites is ``much slower'' than
expected in their system. They attributed this observation to
non-specific interactions between such metabolites and proteins. Maybe
aggregation also contributed to their slower diffusion but it was not
evident during their \SI{140}{\nano\second} simulation.

>>>>

While the structure and dynamics of biomolecules is well characterized
\textit{in vitro}, the understanding of the influences of crowded
environments \textit{in vivo} are still evolving.  Techniques such as
nuclear magnetic resonance~\cite{reckel2007,pielak2008} and
fluorescence spectroscopy~\cite{ignatova2004,xie2008,English2011} are
among the most relevant to the field due to their ability to probe
cells in a non destructive way. Another essential class of methods
come from computational modeling and simulation. By extrapolating the
advances in computational power in the last decades to the future, it
was estimated that the atomistic simulation of an entire
\textit{Escherichia coli} bacterium for \SI{1}{\nano\second} will be
possible in 15 years from now~\cite{vanGunsteren2006a}.
% {\bf THAT WAS 13 YEARS AGO. WHAT IS THE STATE OF THE ART?} {\color{blue} The paper predicts that simulating a whole E. coli bacterium with $10^{11}$ atoms for 1 ns will be possible in 2034, thus the "15 years from now" in our text. That was meant as an introduction to the simulation of big systems. The evolution of computational models to study crowing and the state-of-the-art is discussed in the next paragraph. Maybe we can move this phrase to the beginning of the next paragraph }

@@

\subsection{Analyses}
For statistics, the average and standard error of the three trajectories are reported. For values that
are specific to each chain, we used the average over the individual
chains in each trajectory of the replicas. Additionally, since there
is more than one copy of some crowders in the cytoplasm models,
average values and standard errors are calculated considering each copy of each replica. As in the dilute system, separate chains of each copy
of the crowders were considered as independent samples when running
analyses that focus on one single chain. The first half of all
simulations was discarded as equilibration time and analyses used only
the second half.

Analyses were done using GROMACS tools after removing artifacts
generated by periodic boundary conditions from the trajectories. A
Mean Square Displacement (MSD) analysis was performed to calculate the
translational diffusion coefficient, which were extracted by a linear
fit to MSD by averaging blocks with a length of $10\, ns$ for dilute systems and $100\, ns$ 
for cytoplasm system~\cite{Allen1987a}. In principle, diffusion
coefficient needs to be corrected for finite size
effects~\cite{Yeh2004,Abraham2018}. Due to relatively large simulation boxes
this correction is negligible. 
% {\bf NOT FOR PROTEINS THAT DIFFUSE
  % SLOWLY!}. {\color{blue} The correcion in Yeh2004 is derived for cubic simulation boxes, in our single molecule simulations we have non-cubic boxes, one needs to derive the correction from Eq 11 in Yeh2004. My Mathematica skills are rusty now, could you do that? If you think it's absolutely necessary} 
Root Mean Square Deviation (RMSD) and Root Mean Square
Fluctuation (RMSF) calculations considered the C$\upalpha$ atoms only for analysis in each trajectory.
% {\bf ARE YOU SURE? THE DEFAULT IS TO TAKE THE AVERAGE STRUCTURE. OR DO  YOU MEAN THE STRUCTURE FOR FITTING?} {\color{blue} I checked and indeed we used the average structure calculated with the second half of the trajectories. I removed "the reference frame for RMSF was the midpoint of the time interval" from the text. The information about the second half of the trajectory is in the previous paragraph, which is about statistics}. 
The chain interface area of a given oligomer in a given
frame was calculated as the difference between the solvent exposed
surface area (SASA) of the oligomer in that frame and the sum of the
SASAs of each of its chains independently in that same frame. Other
analyses, such as box volume and Radial Distribution Function (RDF),
followed standard procedures.

@@

\begin{table}[H]
\centering
\caption{Protein, PDB ID, number N of proteins in the simulation. 
Fraction of the total abundance of non-ribosomal proteins in the cytosol of {\em
    E. coli} K12 and oligomeric state of each protein that was
  selected to compose our cytoplasm model.}
\label{tbl:protein_fraction}
\begin{tabular}{ccccc}
\hline
Protein & PDB & N & Fraction [\%] & State\\
\hline
Elongation factor TU (TufA) & 1DG1~\cite{Abel1996}       & 6 & 19.7 &  dimer \\
Cobalamin-independent methionine synthase (MetE) & 1U22~\cite{Ferrer2004}     & 7 & 11.6 &  monomer \\
Isocitrate dehydrogenase (IcdA) & 1P8F~\cite{Mesecar2000}    & 2 & 4.7  &  dimer \\
Alkyl hydroperoxide reductase subunit C (AhpC) & 1YEP~\cite{Parsonage2005}  & 1 & 4.1  &  decamer \\
Cold-shock protein (CspC) & 1MJC~\cite{Schindelin1994} & 3 & 4.0  &  monomer \\
Pyrophosphatase (Ppa)  & 2EIP~\cite{Kankare1996}    & 1 & 2.9  &  hexamer \\
Glyceraldehyde 3-phosphate dehydrogenase A (GapA) & 1S7C~\cite{ShinXXX}        & 1 & 2.1  &  tetramer \\
Enolase (Eno)  & 1E9I~\cite{Kuhnel2001}     & 1 & 1.9  &  dimer \\
\hline
Total &                           & 48& 51.1 & \\
\hline
\end{tabular}
\end{table}

@@

\subsubsection{Structural integrity}
The structure of the individual chains of the crowders that were used
in our cytoplasm model were not affected to a great extent by the
crowded environment. The values of their root mean square deviation considering only
their C$\upalpha$ in the cytoplasm model increased by less than 11\% when compared to the dilute condition, except for
TufA, MetE and IcdA, which have RMSD values 105, 25 and 33\% higher in
the crowded environment than in the dilute condition (Fig.~\ref{fig:structural_integrity_chain}A). 
Visual inspection of the final frames of the simulations of these crowders in the cytoplasm model and in dilute condition revealed that, for TufA, the conformational differences are on the $\upbeta$-hairpin around residues 40-62. This region is called Switch I and is known to be flexible and to display conformational changes due to interactions with the ribosome or other partners~\cite{Abel1996}. For MetE, there are differences in the conformation of the loop around residues 450-460 and in the C-terminal $\upalpha$-helices. This loop is known to be flexible and was not modeled in the crystallographic structure due to such flexibility~\cite{Ferrer2004}. For IcdA, the differences are located at the N-terminal coil formed by residues 1-8.

@@

\subsubsection{Structural dynamics}
% {\bf THIS PARAGRAPH REPEATS AND CONTRADICTS ITSELF. IS FLEXIBILITY
%   AFFECTED OR NOT? FROM THE GRAPH I WOULD SAY THE THE FIVE PROTEINS
%   NOTED BELOW ARE MUCH MORE FLEXIBLE, NOT SLIGHTLY. ONE WAY OF
%   QUANTIFYING THIS IS TO COMPUTE THE AVERAGE OF THE MEAN SQUARE
%   FLUCTUATION OVER THE WHOLE PROTEIN, THAT IS BEFORE TAKING SQUARE
%   ROOTS OF COURSE AND PLOTTING THAT IN A BAR GRAPH.} {\color{blue} Overall, flexibility (meaning the values of RMSF for each residue) is affected in some cases, but the flexibility profile (meaning the overall shape of the RMSF plot) is not. Maybe that was the source of the apparent contradiction. I changed the text to clarify that. I also removed words such as "slightly" and "small" from the text.}

@@

We found that completely protonating the phosphate groups of ATP and
FBP is enough to prevent their aggregation with Mg$^{2+}$. While RDFs
show that ATP$^{-3}$ and FBP$^{-4}$ aggregate around Mg$^{2+}$
(Fig.~\ref{fig:avoiding_aggregation}A), this is not observed for
ATPH\textsubscript{3} and
FBPH\textsubscript{4}(Fig.~\ref{fig:avoiding_aggregation}B-C).  
% {\bf
%   WERE ANY INTERMEDIATE PROTONATIONS TESTED? E.G. FBPH2(2-) AND ATPH(2-)?
%   COMPLETELY PROTONATING IS UNPHYSICAL AS WELL AT THE PH STUDIED. FOR E COLI THE PH SHOULDBE ROUGHLY 7.4 https://en.wikipedia.org/wiki/Cytosol} {\color{blue}I didn't try intermediate protonations, but this can be done in about 1 week if necessary. The physiological states of FBP and ATP at pH 7.4 would be the ones we used originally in the soup. So, in this sense, any protonated state could be called unphysical or unrealistic. We discuss the tradeoffs of using this unphysical protonated state in the discussion section}

@@

\section*{Discussion}\label{sec:dissc}
The main difference between the behavior of the macromolecules that
compose our model in the crowded system and in the dilute condition is
their translational diffusion coefficient, which drops by around
85\% for the proteins and 93\% for the tRNA
(Fig.~\ref{fig:translational_diffusion}A). The slope of the line
generated by fitting a linear regression model to values of
$D_{cyto}/D_{dil}$ is close to zero (slope $= 0.00028$), showing that
the drop in diffusion coefficient is independent of the size of the
macromolecules. We found that the aggregation of ATP$^{-3}$ and
FBP$^{-4}$ around Mg$^{2+}$, which was used as counter-ion for tRNA,
leads to an exaggerated confinement of the tRNA molecules.  Therefore,
tRNA is considered as an outlier in the duffusion calculations. In
fact, the slope of the linear regression line fitted to
$D_{cyto}/D_{dil}$ is reduced by by 50\% and gets even closer to zero
(slope $= 0.00014$) after removing the diffusion coefficient of tRNA
from the data. These data are in agreement with experimental results
showing that the translational diffusion coefficient of Green
Fluorescent Protein (GFP) in {\em E. coli}, as measured by
fluorescence recovery after photo-bleaching (FRAP), decreased 90\%
when compared to {\em in vitro}
measurements~\cite{Elowitz1999,Konopka2006}.

% {\bf IT MAY BE NECESSARY TO DISCUSS RMSF HERE AS WELL} {\color{blue} This first paragraph is focused on validation of the cytoplasm model by comparison with experimental results, which are available for the translational diffusion coefficient. We don't have specific experimental data that we can compare our RMSF data to. Should we add RMSF here anyway? There is a discussion about our RMSF results some paragraphs ahead in which we compare our data with general trends that were experimentally observed.}

@@

Previous
all-atom simulations of large scale cytoplasm models used parameters from the CHARMM family of
force fields~\cite{Yu2016a}. In this work we use a modified version of
the AMBER FF99SB force field in which the solvent-solute interactions
are 10\% stronger~\cite{Best2014a} to study crowding effects on a
cytoplasm model. This force field was chosen because it was corrected
to reproduce experimental data when there are many proteins in the
same simulation box. This force field or similarly adjusted one were also used for studying crowding effect on simpler systems of high concentration of proteins~\cite{Nawrocki2017a,nawrocki2019,Bashardanesh2019a}. All-atom explicit solvent molecular dynamics simulations have been reported for large-scale cytoplasm models of
\textit{Mycoplasma genitalium} composed of 103- and 12-million atoms
that were simulated for 20 and 60 \SI{}{\nano\second},
respectively~\cite{Yu2016a}. The cytoplasm model described in this
work has 1.5 million atoms and was simulated for the total of
\SI{3}{\micro\second}, an unprecedented time scale to study crowding effects on a heterogeneous cytoplasm model in atomic detail.

Three crowders (TufA, MetE and IcdA) displayed greater deviation from
their crystallographic structure in the cytoplasm model when compared
to the dilute condition, indicating that there was some degree of
local unfolding
(Fig.~\ref{fig:structural_integrity_chain}A). Interestingly, oligomers
were marginally less stable in the cytoplasm model than in the dilute condition.
(Fig.~\ref{fig:structural_integrity_chain}B) and the flexibility
profiles calculated considering the C$\upalpha$ for each chain of the
elements of our cytoplasm model show that, in the crowded condition,
most of the proteins (TufA, MetE, AhpC, CspC and Ppa) are more flexible than in the dilute condition (Fig.~\ref{fig:rmsf}). This
is in agreement with previous simulations~\cite{Feig2011} and
experiment~\cite{miklos2011,Wang2012b} showing that crowders can
destabilize the native structure of proteins due to the numerous
unspecific short-lived interactions that are formed between them in a
crowded environment. A study of protein properties at increasing
concentration showed only few interactions between proteins of the
same type~\cite{Bashardanesh2019a}. {\color{blue} We highlight that there are no specific interactions described between the proteins that were used in our cytoplasm model.} {\bf do we expect specific interactions between the proteins in our cyto model? In that case write that with references, otherwise write that there are no known specific interactions between these proteins.} {\color{blue} The only specific interaction we antecipate between the components of the soup is that TufA interacts with tRNA (PDB ID 1TTT is an example of such complex). However, since we are ignoring tRNA in our analyses, I did't mention it. PS: I checked and the TufA-tRNA complex is not present in the last frames of our replicas.}

Magnesium cations were added to our cytoplasm model as counter-ions
for tRNA and ATP. However, as the simulation progressed, FBP and ATP
aggregated around Mg$^{2+}$ and, by consequence, around tRNA
% {\bf,
%   effectively removing the counter ions from the RNA. IS THAT
%   CORRECT?} {\color{blue} No, Figure \ref{fig:tRNA_aggregation} shows that Mg$^{2+}$ is still concentrated around tRNA in the soup }. 
  After identifying this problem, we used simulations of
small systems containing only the metabolites, Mg$^{2+}$ and water to
test different strategies to prevent aggregation in future studies
using long simulations of cytoplasm models. We found that protonating
the phosphate-containing metabolites is enough to reach this goal
(Fig.~\ref{fig:avoiding_aggregation}). Even though ATPH$_3$ and
FBPH$_4$ are not the biologically relevant forms of these molecules in
physiological pH, using their protonated forms may be an acceptable
compromise between parametrization complexity and practical
results. The biggest impact of this approach is on long range
interactions of these metabolites with other molecules due to the
neutralization of their net charge. However, molecules in a crowded
environment are restrained to smaller volumes and shorter inter
molecular distances, which mitigates the effect of charge
neutralization. It has been suggested that charged species should
employ scaled charges in order to be compatible with the empirical
water models~\cite{Leontyev2009a,Leontyev2011a}. Due to the high local
density of negative charges in FBP and ATP this might indeed be an
alternative solution, barring use of polarizable
models~\cite{Ponder2010a,Lopes2013a,Ghahremanpour2018b,Walz2018a}.

To the best of our knowledge, there is only one published study on large scale cytoplasm models that
included metabolites with all-atom explicit solvent molecular
dynamics~\cite{Yu2016a}. Although these authors did not report
aggregation, they mention that the translational diffusion of highly
charged phosphate-containing metabolites is ``much slower'' than
expected in their system. They attributed this observation to
non-specific interactions between such metabolites and proteins. Maybe
aggregation also contributed to their slower diffusion but it was not
evident during their \SI{140}{\nano\second} simulation.
